\section{Week 2 (15) Activity Report w/e 14.04.19}
\subsection{Literature research assignment: Distinguishing disks from mergers}
Briefly summarise the key methods and results of the following papers:
\begin{itemize}
    \item \citet{2011ApJ...742...11S} : {The Interstellar Medium in Distant Star-forming Galaxies: Turbulent Pressure, Fragmentation, and Cloud Scaling Relations in a Dense Gas Disk at z = 2.3}
    \item \citet{2016A&A...591A..85B} : {Distinguishing disks from mergers: Tracing the kinematic asymmetries in local (U)LIRGs using kinemetry-based criteria}
    \item \citet{2008ApJ...682..231S} : {Kinemetry of SINS High-Redshift Star-Forming Galaxies: Distinguishing Rotating Disks from Major Mergers}
\end{itemize}

\subsection{Computing \& Data Analysis}
\begin{itemize}
    \item {Received FITS tables of control galaxies from Yanmei. Able to read data using Marvin function OK.}
    \item Generated MaNGA maps for:
    \begin{itemize} 
        \item Stellar velocity
        \item Gas velocity
        \item D$_n$4000 spectral index
        \item Emission line strengths
    \end{itemize}
    \item Investigated cost of student licence for IDL. Pricey.
\end{itemize}

\subsection{Other reading}
\begin{itemize}
\item \citet{2004ApJ...609..683T} : {Field E+A Galaxies at Intermediate Redshifts ($0.3 < z < 1$)} : PSB galaxies.
\item \citet{2009MNRAS.395..144W} : {Post-starburst galaxies: more than just an interesting curiosity} : {Post-starburst galaxies in the VVDS : PCA of the 4000\AA break.} : Are gas-rich mergers an important mechanism for the build-up of the red sequence since $z\sim1$.
    \item \citet{2004ApJ...608..752B} : {Nearly 5000 Distant Early-Type Galaxies in COMBO-17: A Red Sequence and Its Evolution since $z\sim1$} : Galaxy colour bi-modality.
\item \citet{1972ApJ...176....1G} : {On the Infall of Matter Into Clusters of Galaxies and Some Effects on Their Evolution} : Ram pressure stripping.
\item \citet{2006MNRAS.366..787K} : {Kinemetry: a generalization of photometry to the higher moments of the line-of-sight velocity distribution}
\item \citet{1997A&A...325.1025P} : {Indicators of star formation: 4000 {\r{A}} break and Balmer lines.} : Dn4000 and equivalent width of Balmer lines.
\end{itemize}