\section{Week 7 (20) Activity Report W/e 19.05.19}

\subsection{Computing \& Data Analysis}
Much effort has gone into getting the Radon code to run on the AstroLab machines, remotely.
\begin{itemize}
    \item Now happy with remote access, IDL setup and \texttt{!PATH} IDL Astro and Cayode Libraries configuration. 
    \item Received revised Radon code scripts from VW. Now \texttt{example.pro} runs and generates output as a \texttt{PostScript} file. PS file retrieved to the local machine  and re-sized for use in a document figure. 
    \item Created notebook \texttt{Marvin-save-map-as-array}. The purpose of this notebook is to prepare Marvin velocity maps: \texttt{stellar\_vel} and \texttt{emline\_gvel\_ha\_6564} in array form for input to the Radon transform code of \citet{2018MNRAS.480.2217S} The note book follows the examples given at: \url{https://sdss-marvin.readthedocs.io/en/stable/tools/map.html}. 
    \item Maps and masking principles reviewed and understood.
    \item Maps download to disc in various formats, text, CSV etc.
    \item Attempted to pass a map data array to the Radon code. Unsuccessful. Need to clarify the required data format that \texttt{ds\_radon} expects: a text array, an IDL \texttt{IMAGE} object, or whatever. This is a sticking point at the moment.
\end{itemize}

\subsection{Dissertation}
\begin{itemize}
    \item Started thinking about generating an outline for the report.
    \item Reviewed the HWU template. This looks: well structured in terms of file organisation and hierarchy.
    \item Does St Andrews have a standard masters thesis format or template?
    \item Commenced a basic report outline using the MNRAS template.
\end{itemize}
