\section{Week 4 (17) Activity Report W/e 28.04.19}

\subsection{Computing \& Data Analysis}
\begin{itemize}
    \item Received FITS files containing control sample galaxy data for cPSB and rPSB samples. Read these into Python/Pandas DataFrames OK.    
    \item Identified duplicate entries in above mentioned control galaxy data files.
    \item Looked at the Radon code method. Radon also requires IDL. So Radon has not been not pursued further at this stage.
    \item Received full MPL-8 galaxy listing with calculated kinematic stellar and gas PAs and observation quality flags set. Imported this data into Python/Pandas OK.
    \item {Plotted histogram distributions of misaligned (PA $>$ 30$\degree$) cPSBs and rPSB.}
    \item Received Kinemetry PA output plots for cPSB (30) and rPSB (37) galaxy samples.

\end{itemize}
\subsection{Reading}
\begin{itemize}
    \item \citet{2019ApJ...872...76N} : {Accurate Identification of Galaxy Mergers with Imaging}
    \item \citet{2019arXiv190100856W} : {The Data Analysis Pipeline for the SDSS-IV MaNGA IFU Galaxy Survey: Overview}
    \item \citet{2019MNRAS.483..172D} : {SDSS-IV MaNGA: signatures of halo assembly in kinematically misaligned galaxies}
    \item \citet{1996ApJ...466..104Z} : {The Environment of ``E+A'' Galaxies} 
    \item \citet{2017MNRAS.466..798C} : {Improving the full spectrum fitting method: accurate convolution with Gauss-Hermite functions}
    \item \citet{2004PASP..116..138C} : {Parametric Recovery of Line-of-Sight Velocity Distributions from Absorption-Line Spectra of Galaxies via Penalized Likelihood}
    \item \citet{2005MNRAS.357..937G} : {266 E+A galaxies selected from the Sloan Digital Sky Survey Data Release 2: the origin of E+A galaxies}
    \item \citet{10.1093/pasj/55.4.771} : {H$\delta$-Strong Galaxies in the Sloan Digital Sky Survey: I. The Catalog}
\end{itemize}